%!TEX root = ../DDD.tex

\chapter{Scope}
\label{chp:scope}

\section{Identification}
This document is applies to AreaAware.
A system which goal is to provide a tool for a better and more effective handling of a civilian crisis.

The system will provide the commanders with an overview of the crisis in hand through a common operational picture(COP), where every task to be resolved can be identified and the emergency responders locations can be tracked.
This should make it easier to handle and evaluate a civilian crisis. 
The system will also provide a better communication between the multiple Commanders and Emergency Responders during a crisis.

AreaAware will communicate over the defined standard network used in these scenarios.
In Denmark this network is called SINE which follows the international standard TETRA used for communication during crisis situations world wide.

AreaAware can be adapted to any specific network instead of SINE easily only by changing the interface of AreaAware.


\section{System overview}
The system of interest will communicate with the already employed SINE network used by the emergency management agency.

The system will facilitate the commander in:
\begin{itemize}
    \item Give a demographic overview of the crisis area.
    \item Let the Commanders locate events, things of interest and ERs in the area.
    \item Let the Commanders send commands to other Commanders and ERs in the area.
\end{itemize}

The system will let commanders plug their own laptop(not provided) to the AreaAware HQ.
By plugging their laptop to the AreaAware HQ they will be allowed access to the common operation picture through a web application. 
The web application will be accessed through a browser installed on the customers own laptop.

\section{Document overview}
This document describes how AreaAware and the subsystems within will be structured to satisfy the requirements defined in the following documents:
\begin{itemize}
    \item System Requirement Specification for AreaAware HQ, Document ID: AreaAware-SRS-20160214-01-02
    \item System Requirement Specification for AreaAware Dismounted, Document ID: AreaWare-DISSRS-20160214-01-02
\end{itemize}

Chapter \ref{chp:system-wide} describes system wide decisions regarding behavioral design and design of system components.
After this chapter \ref{chp:architectural} gives an architectural design of the AreaAware system, which identifies system components, describes how the system components interact.
Section \ref{sec:arch_interface} refers to another document, Interface design, which defines the interface design between the system components describe within this document. \\
Finally the document provides an overview of requirements traceability mapping the system components to the requirements specified in the documents mentioned above.

\section{Referenced documents}
In this table all the referenced documents will be listed.

\begin{tabular}{b{6cm} b{7cm}}
	\textbf{ID} & \textbf{Document name} \\
	\hline
	\rtm & Requirement Traceability Document \\
\end{tabular}