\label{chp_scope}
\chapter{Scope}

\section{Identification}
this document will cover the interfaces for the AreaAware HQ and AreaAware Server. The interfaces for AreaAware Dismounted are described in a separate documented, which is referenced in relevant chapters.
AreaAware will give the Emergency Commander and Field commander a Common Operations Picture. The system will communicate with devices already used in civil crisis scenarios. AreaAware will communicate over the defined standard network used in these scenarios. 
This network is called SINE(Sikkerhednetværket) and it follows an international standard for communication called TETRA which is used during crisis situations world wide.

\section{System overview}
The system of interest will communicate with the already employed system used by Emergency Responders. Emergency Responders use the SINE network during crisis situations. The system will facilitate the Emergency Commander in:

\begin{itemize}
	\item  Give a demographic overview of the crisis area
	\item Let the commander locate events, things of interest and actors in the area.
	\item Let the commander send commands to actors in the area.
\end{itemize}

The system will let Emergency Commanders by their own computer systems(not provided) to be able to connect via a webapplication and then get access by this webapplication. They will be allowed access to the Common Operations Picture through a web application. The web application will be accessed through a browser installed on the customers own computer systems.


\section{Document overview}
This document will describe the internal and external interfaces of the system.

Each interface will be described throughout this chapter. Each interface will be given a unique id. If the interface is internal the id will be on the form \emph{II-XX}. If the interface is external the id will be given on the form \emph{EI-XX}. Diagrams will support the understanding of interfaces and each interface description will be given a name and version number.

The interface description will be divided up into subsystems: AreaAware HQ chapter \ref{sec:areaAwarehq} and AreaAware Server chapter \ref{sec:areaAwareserver}.

AreaAware HQ provides the Emergency Commander with a Common Operations Picture (COP). The COP also allows the Emergency Commander to communicate with Emergency Responders.

AreaAware Server provides a high speed server solution for communication between AreaAware HQ, AreaAware Dismounted and already used solution. This server communicates with AreaAware HQ, AreaAware Dismounted and other already implemented solutions through the SINE network. The AreaAware Server also makes it possible to extend the network capabilities of SINE through the use of a high speed internet connection.
