\label{chp_operations}
\chapter{Operations and Support Description}
This chapter describes the missions, users and general operation and support description of the system.

\section{Missions (Primary/Secondary)}
Primary missions:
\begin{enumerate}
	\item To gather information and events from multiple Emergency Responders to establish situational awareness.
	\item Display large amounts of static and dynamic data to give a COP for the Emergency Commanders and Field Commanders to make the right decisions.
	\item Dispatch orders from the Emergency Commanders or Field Commanders to the different Emergency Responders to deal with the given situation. Send messages between Emergency Commanders, Field Commanders and Emergency Responders.
\end{enumerate}

\noindent Secondary users:
\begin{enumerate}
	\setcounter{enumi}{3}
	\item Deploy Dismounted COPs for Field Commanders to make individual decisions.
\end{enumerate}

\section{Users and Other Stakeholders}
\noindent Primary users:
\begin{itemize}
	\item Emergency Commanders (ECs): \\
	These Commanders are located in the mobile Headquarters are able to utilize the full capabilities of the COP. Can receive events registered using employed platforms from various actors and send information to these platforms.
	\item Field Commanders (FCs):\\
	Emergency Commanders who are located in the field. Will have access to a condensed version of the COP on a hand-held device, called the Dismounted COP.
\end{itemize}
	
\noindent Secondary users:
\begin{itemize}
	\item Emergency Responders (ERs):\\
	Is able to register events using the currently employed platforms. Is also able to receive information on the same platforms. These include the police, armed forces, hospitals, emergency management etc.
\end{itemize}

\noindent Stakeholders:
\begin{itemize}
	\item The State/society: \\
	Is interested in the system as the state will likely be the ones utilizing the system and its capabilities to handle an emergency situation. The entire system is being implemented to provide a better service in emergency situations for society.
	\item Subcontractor:\\
	The subcontractor is tasked with developing the Dismounted COP for Field Commenders.
\end{itemize}


\section{Policies, Assumptions and Constraints | Policy, Assumption, Constraint}
\textbf{Policies:} \\
A common policy for communication will have to be provided for secondary actors.. 
Several policies, laws and restrictions that are in place under everyday situations for each of the secondary actors are suspended under the emergency situations where the system is to be used. Therefore, these are not taking into account in this document.\\

\noindent \textbf{Assumptions}
\begin{enumerate}
	\item The subcontractor will deliver a satisfactory product, satisfying the specified requirements for the Dismounted COP.
	\item It is possible for the Emergency Responders to implement features making it possible to register events to and receive orders from ECs.
	\item The mobile HQ, hand-held devices of the FCs and the Emergency Responders’ separate systems are compatible with the SINE network.
	\item Connection can be established to the SINE network for all relevant devices, allowing communication.
\end{enumerate}

\noindent \textbf{Constraints}
\begin{enumerate}
	\item The system is developed for Denmark, where the SINE network is deployed.
\end{enumerate}

\section{Operation Description | Operating Concept (OpCon), Employment Modes}
\subsection{Operational Concept}
The figure below show the overall principle of the AreaAware system, and how it is connected the various users and subsystems.
%\myFigure{arg1}{arg2}{arg3}{arg4}

The AreaAware system contain two parts, the Mobile HQ COP and the Dismounted COP. The Mobile HQ COP provide situational awareness for the Emergency Commanders inside the EHS, and the Dismounted COP provide situational awareness for the Field Commanders inside the disaster zone. AreaAware use the SINE network for communication with the Emergency Responders. This way the Emergency and Field Commanders are able to get information and issue orders to any part of the persons involved in resolving a disaster situation.

\subsection{Employment Modes}
Idle: The system is not in active use, but is ready for fast deployment is case of a large-scale civil emergency.\\

\noindent Deployment: The Mobile HQ COP is deployed with the EHS in the area affected by a disaster, and communication is established with all involved Emergency Responders and Field Commanders using SINE.\\
 
\noindent Live disaster management: Gather information from Emergency Responders, present these data for the Emergency and Field Commanders, and send commands to the Emergency Responders for solving the disaster.\\

\noindent Emergency power mode: A mobile power source is used, when the general power grid is offline.\\

\subsection{Scheduling and Operations Planning}
The HQ- and Dismounted COP’s will be a part of the Danish emergency Management Agency’s mobile equipment for disaster handling, and will have to be ready for deployment 24/7.

\subsection{Operating Environment}
\noindent \textbf{Geographic Area:}
The AreaAware system can be deployed in any geographic area affected by a major disaster, but for simplicity it is constrained to be in Denmark.

\noindent \textbf{Environmental Conditions:}
The Mobile HQ COP is located with the ECs inside the EHS. The vehicle/station will shield the system against bad weather conditions and ect. \\

The Dismounted COP can experience a wide range of environmental scenarios. This include temperature ranges, humidity levels, weather conditions and ect. The Field Commanders is located close to the action inside the disaster zone. It is therefore important that the Field Commander can get a overview and make quick decisions in stressful situations.

\subsection{Threats and Hazards}
As AreaAware is deployed in a disaster situation there are potential hazards relating to the environment. It is likely that the system will experience extreme weather situations like hurricanes and floods.

Data security is important for the communication between the actors in the system. It would e.g be a problem if a group of terrorist could track the police’ movements by hacking the AreaAware communication network.

\subsection{Interoperability with Other Elements}
The Mobile HQ COP have a general interface for a wide range of equipment, for supplying situational awareness on the ECs. The Mobile HQ COP also have an interface to the SINE network and an internet connection. The Dismounted COP will also need an interface to the SINE network for communication.

\newpage
\section{Product Support Description}
This section will describe the support plan of the system, including the extent and duration of support and the existence of live-support. 

\subsection{Software Warranty}
A Software Warranty Service is part of the Statement of work for the system \cite{bibid}. The Software Warranty Service is cited below: \\

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
\textit{"Software Warranty Service consists of:
Defect Reporting. For Critical Defects, the Customer will have 24x7 access to the Service Centre by e-mail or phone to request defect repair, as described below. “Critical Defect means that the application is down or is at high risk, business functions cannot be conducted, or the Customer is experiencing continual failures or data corruption as a result of the defect. To report non-critical defects, the Customer will have e-mail or phone access to the Service Centre during the Principal Period of Maintenance (”PPM”), which is 8:00 a.m. to 5:00 p.m., local time, Monday through Friday, excluding local holidays.} \\

\textit{Defect Repair. Defect repair includes verification of the existence of a defect, determination of the severity or impact of the defect, and determination of the conditions under which the defect may recur. The Company will, at its option:}
\begin{itemize}
	\item \textit{For a Critical Defect, commence action within a 2-shift hour response window using  commercially reasonable efforts to provide an immediate fix or temporary solution of, or workaround to, the defect.}
	\item \textit{For a non-critical defect, commence action within an 8-shift hour response window to provide either the action described for a Critical Defect or a statement that the defect will be corrected in a software product revision or a future software release.}
	\item \textit{Provide a statement that the Software operates as described in then-current user documentation or that the defect arises when such Software is used other than in a manner for which it was designed. For Software added to an installed System, warranty service must be upgraded to the same software support plan, if any, as that of the Software already installed on that System. Customer will pay the difference between standard warranty and upgraded warranty service."}
\end{itemize}
\end{minipage}

Furthermore, an extended 24x7 support service is offered to the customer, where the contractor is continually offering training, equipment and information support.
The Six Facets of Readiness \cite{bibid} https://www.uscg.mil/acquisition/newsroom/pdf/msam.pdf will be used to describe the support of the system:

\subsection{People}
As the system is not directly involved with any physically demanding task, there is no need to consider the medical care of the users of this system.

\subsection{training}
The users of this system will have a user manual to refer to, describing all the features of the system in a user-friendly manner. If need be, the user can call our 24x7 support with questions.

\subsection{Equipment}
The configuration control of the system is maintained by the actors, with cooperation of the CSP. If configuration control of the system is not maintained, a user manual, as well as 24x7 support according to the Software Warranty. 

\subsection{Support}
In accordance with the Software Warranty, access is available 24x7 to the service center, where the customer can request defect repair. There are two types of defect requests:
\begin{itemize}
	\item Critical Defect, for which an action must to commenced within a 2-shift hour response window, using reasonable efforts. This action must provide an immediate fix, temporary solution or workaround to the defect. This is available for 24x7 support.
	\item Non-critical defect, where an action is required to commence within an 8-shift hour response window. This action must provide the service as for a Critical Defect or a statement has to be released describing that it will be fixed in a future release. \\
	The non-critical defect can be reported during the Principal Period of Maintenance, as described in the Software Warranty.
\end{itemize}

\subsection{Infrastructure}
The current infrastructure will support the system. In emergency situations, where the system has to be deployed, precautions will be made to ensure the required infrastructure.
In case of an earthquake, or other disaster, making conventional infrastructure virtually inaccessible, the mobile HQ can be transported by helicopter etc. to the area where it is needed.

\subsection{Information}
Information will be maintained by the development team, who will keep supporting and maintaining the system for an agreed-upon amount of time.

\section{Potential Impacts}
This system have the potential to significantly improve the emergency response service provided by various actors in a large-scale civil emergency situation. This is done by providing intelligence for assigned commanders in the form of a COP and giving them the possibility receive events from and dispatch orders to ERs. ERs will have to implement a feature in the respective currently employed systems in order to enable communication with the suggested system. 
The suggested system will be compatible with the SINE network in Denmark, securing a stable connection between devices even in severe emergency situations, where other networks fail.






