%!TEX root ../minutesOfMeeting.tex
%
\thispagestyle{fancy}
\chapter*{Minutes of meeting}


\section*{Call to order}
A meeting between representatives Problematic and the customer of the AreaAware system.
\textbf{Location:} Problematic at Finlandsgade 22 8200 Aarhus N, Denmark.\\ Building: Edison Room E235.\\
\textbf{Date:} Friday 19-feb-2016. \\
\textbf{Time:} 11:00-11:30.
\section*{Attendees}
\textbf{From Problematic:} Jens Frost Lunding, Simon Bækkegaard, René Rotvig Jensen \& Kim Lykke Johansen.\\
\textbf{Customer:} Casper Thule Hansen.\\\\
\textbf{Not present:} From problematic: Simon Østergaard Kristensen, Jeppe Blixenkrone-Møller,, Kristoffer Sloth Gade \& Ivan Bjerring Hansen.\\\\
\textbf{Meeting Moderator \& Time keeper:} Kim Lykke Johansen. \\
\textbf{Minutes Taker:} Kim Lykke Johansen.

\section*{Minutes of meeting}
\begin{itemize}
    \item From now on minutes of meeting will be itemized with correction IDs.
    \item With each minutes of meeting will follow a matrix of corrections for tracing the issues mentioned in meetings to the changes in documents.\\\\
    \item Mintutes of meetings from Friday 2016-02-12 needs front page, document ID and version history. \textbf{Correction ID: CID-AA-20160219-01}
    \item Redeliver minutes of meeting from Friday 2016-02-12 on Wednesday 2016-02-24.
\end{itemize}

\newpage
\section*{Feedback on PDD}
\begin{itemize}
    \item Throughout the document the word "Commander(s)" is used, it is not clear who this commander is (Field or Emergency or both?).\\ \textbf{Correction ID: CID-AA-20160219-02}
    \item Section 1.1 and 1.2 "Actors" and "Emergency management actors" choose one and stick with it.\\ \textbf{Correction ID: CID-AA-20160219-03}
    \item Section 2.1.1 Text mentions "An Event Log keeps track..." when describing the Event History. Check the rest of the document for same error.\\ \textbf{Correction ID: CID-AA-20160219-04}
    \item Section 2.2 and figure 2.2 the customer would like a dial function. \\ \textbf{Correction ID: CID-AA-20160219-05}
    \item Section 2.4 should contain design choices for Dismounted as well for the customer to see. \textbf{Correction ID: CID-AA-20160219-06}
    \item Section 3.1 the sentence just above the figure needs to be rewritten. \\ \textbf{Correction ID: CID-AA-20160219-07}
    \item Figure 3.1 needs a descriptive text and a ref to the figure from this text.\\ \textbf{Correction ID: CID-AA-20160219-08}
    \item Section 3.1 for all tables; references to document IDs should be gathered with latex references, to only update once when IDs changes.\\ \textbf{Correction ID: CID-AA-20160219-09}
    \item Section 3.2 first sentence should be rewritten.\\ \textbf{Correction ID: CID-AA-20160219-10}
    \item Figure 3.4 is not referenced anywhere in the text.\\ \textbf{Correction ID: CID-AA-20160219-11}
    \item Section 3.3 Todo needs to be resolved.\\ \textbf{Correction ID: CID-AA-20160219-12}
\end{itemize}

\newpage
\section*{Feedback on Interface}
\begin{itemize}
    \item Front page lines continues forever. \\ \textbf{Correction ID: CID-AA-20160219-13}
    \item Table of contents is in danish. \\ \textbf{Correction ID: CID-AA-20160219-14}
    \item Section 2.1 it is not clear if this document covers the whole system or just HQ. \\ \textbf{Correction ID: CID-AA-20160219-15}
    \item Section 2.1 it is not clear if it is only one of the commanders that gets the operation picture. \\ \textbf{Correction ID: CID-AA-20160219-16}
    \item ICCs should appear in the glossary. \\ \textbf{Correction ID: CID-AA-20160219-17}
    \item Figure 3.1 should include the server. Move the figure in front of description tables. \\ \textbf{Correction ID: CID-AA-20160219-18}
    \item Figure 3.2 should include the HQ. Move the figure in front of description tables. \\ \textbf{Correction ID: CID-AA-20160219-19}
    \item EI-03 It's called "Center for Bered..." \\ \textbf{Correction ID: CID-AA-20160219-20}
    \item II-02 Last sentence should be rewritten. \\ \textbf{Correction ID: CID-AA-20160219-21}
    \item Missing interface description for Dismounted. \\ \textbf{Correction ID: CID-AA-20160219-22}
\end{itemize}


\section*{Further details desired for DDD}
Could include more elaboration on the data formats (packages etc.), define the overall structure of the software, define what kind of server and what commercial internet is (xml or ?).\\
Each block of the architecture should be opened up and described.

\newpage
\section*{Comments on resubmitted deliverables from last week}
\begin{itemize}
    \item SRS HQ: Revision traceability, reference to the minutes of meeting where changes are from. \\ \textbf{Correction ID: CID-AA-20160219-23}
    \item SRS HQ: Temperature requirement not fixed since last meeting. Should be used in an indoor environment. \\ \textbf{Correction ID: CID-AA-20160219-24}
    \item SRS Dismount: Revision traceability, reference to the minutes of meeting where changes are from.
    \\ \textbf{Correction ID: CID-AA-20160219-25}
    \item SRS Dismount: Figure label in danish, says "Figur".
    \\ \textbf{Correction ID: CID-AA-20160219-26}
    \item Conops: Document ID should match the other documents.
    \\ \textbf{Correction ID: CID-AA-20160219-27}
    \item SEMP: Should describe the payment, how to be paid? All up front? \\ \textbf{Correction ID: CID-AA-20160219-28}
    \item SEMP: How many developers do we assign to the project.
    \\ \textbf{Correction ID: CID-AA-20160219-29}\\\\
    
    \item All of this should be resubmitted again.  
\end{itemize}

\section*{General for all documents}
\begin{itemize}
    \item The abbreviation COP is define as multiple things, align this, maybe with latex command. \\ \textbf{Correction ID: CID-AA-20160219-30} 
    \item Traceability matrix should have its own document. \\ \textbf{Correction ID: CID-AA-20160219-31}
    \item The glossary should be common for all documents. \\ \textbf{Correction ID: CID-AA-20160219-32}
    \item The glossary needs to include TETRA. \\ \textbf{Correction ID: CID-AA-20160219-33} 
    \item The references to the Dismounted SRS document ID are inconsistent.
    \\ \textbf{Correction ID: CID-AA-20160219-34}
\end{itemize}

% thule er helt tosset med vores diagrammer
% fede figure og gode ID'er 


\section*{Other business}
\begin{itemize}
    \item The subcontractors are expected to deliver documents to their prime contractor as a part of the interaction within this course. \\
    \item Next meeting: Friday 26th feb at 10:00 in Shannon.
\end{itemize}

