%!TEX root ../minutesOfMeeting.tex
%
\thispagestyle{fancy}
\chapter*{Minutes of meeting}


\section*{Call to order}
A meeting between representatives Problematic and the customer of the AreaAware system.\\
\textbf{Location:} Problematic at Finlandsgade 22 8200 Aarhus N, Denmark.\\ Building: Shannon.\\
\textbf{Date:} Friday 26-feb-2016. \\
\textbf{Time:} 10:00-10:30.
\section*{Attendees}
\textbf{From Problematic:} Jeppe Blixenkrone-Møller, Simon Østergaard Kristensen,  Kristoffer Sloth Gade \& Kim Lykke Johansen.\\
\textbf{Customer:} Casper Thule Hansen.\\\\
\textbf{Not present:} From problematic: Jens Frost Lunding, Simon Bækkegaard, René Rotvig Jensen \& Ivan Bjerring Hansen.\\\\
\textbf{Meeting Moderator \& Time keeper:} Kim Lykke Johansen. \\
\textbf{Minutes Taker:} Kim Lykke Johansen.

\section*{Feedback on Minutes of meeting and Matrix of Correction}
\begin{itemize}
    \item Matrix of Correction should have a more descriptive status, e.g. \emph{rewritten}, \emph{spelling error corrected}, \emph{figured updated}.
\end{itemize}

\newpage
\section*{Feedback on DDD}
\begin{itemize}
    \item Section 1.3: Mentions components, are these the same as the components mentioned in the PVP (document ID: \pvp)? This should be clear.
    \\ \textbf{Correction ID: CID-AA-20160226-01}
    
    \item Section 2.2: Needs a description of the appearance of Dismounted.
    \\ \textbf{Correction ID: CID-AA-20160226-02}
    
    \item Figure 2.2: Web Interface is the same as Web Presenter, change the word choice to Web Presenter.
    \\ \textbf{Correction ID: CID-AA-20160226-03}
    
    \item Section 2.4: D-HQ4 specifies that the system must have a speaker and a microphone. But it is also necessary to specify whether the system is build on a mouse/keyboard interface or a touchscreen.
    \\ \textbf{Correction ID: CID-AA-20160226-04}

    \item Section 3.1.2: Subsections hereof, i.e. web presenter and communication modem, should have a section number as well.
    \\ \textbf{Correction ID: CID-AA-20160226-05}
    
    \item Section 3.1.3: Specify what type of database that will be used.
    \\ \textbf{Correction ID: CID-AA-20160226-06}
    
    \item Under figure 3.6: It says: "Same goes ..." This should be clarify as to what \emph{same} covers.
    \\ \textbf{Correction ID: CID-AA-20160226-07}
\end{itemize}

\newpage
\section*{Feedback on Interface}
\begin{itemize}
    \item General: Missing descriptions of data formats.
    \\ \textbf{Correction ID: CID-AA-20160226-08}
    
    \item II-05: It should be stated that there should be 14 of these.
    \\ \textbf{Correction ID: CID-AA-20160226-09}
\end{itemize}.

\section*{Feedback Verification plan}
\begin{itemize}
    \item Chapter 1 and section 1.1: should be spell checked
    \\ \textbf{Correction ID: CID-AA-20160226-10}
    
    \item Section 2.1 and 2.1.1: Unit test is the same as component test. Change word choice to component test everywhere.
    \\ \textbf{Correction ID: CID-AA-20160226-11}

    \item Section 2.1.2: When is "whenever possible" this is a vague formulation. Rewrite it.
    \\ \textbf{Correction ID: CID-AA-20160226-12}
   
    \item Section 2.1.3: "This is an internal testing fase and does not require a customers approval." Remove this, as it is already specified, or include it in 2.1.1 og 2.1.2
    \\ \textbf{Correction ID: CID-AA-20160226-13}
    
    \item Section 2.2: include system engineers.
    \\ \textbf{Correction ID: CID-AA-20160226-14}
    
    \item Section 2.3: "at least 15". Just remove at least, there is room for 15.
    \\ \textbf{Correction ID: CID-AA-20160226-15}
    
    \item Section 3.1: anomaly goes for every software bug? Give a clear definition of what is considered an anomaly.
    \\ \textbf{Correction ID: CID-AA-20160226-16}
    
    \item Section 4.1: Number 1 and 6, time should be more descriptive.
    \\ \textbf{Correction ID: CID-AA-20160226-17}
    
    \item Appendix A findes to gange.
    \\ \textbf{Correction ID: CID-AA-20160226-18}
    
    \item Appendix Verification template needs a little descriptive text.7
    \\ \textbf{Correction ID: CID-AA-20160226-19}
\end{itemize}.

\newpage
\section*{General for all documents}
\begin{itemize}
    \item Revision history tables are messy, use lines to separate.
    \\ \textbf{Correction ID: CID-AA-20160226-20}
    
    \item Before hand-ins we should do some spell checking.
\end{itemize}

\section*{Resubmit}
It is only necessary to resubmit the ICD.\\
But suggested changes should be implemented in the PDD as well. The customer might want to see the document again.

\section*{More details for Verification plan}
\begin{itemize}
    \item Include dates for test.
    \item Include testing period in time schedule.
    \item Plan for component integration tests.
\end{itemize}

\section*{Other business}
\begin{itemize}
    \item Next meeting: Friday 4th of March kl. 10:00, in Shannon.
\end{itemize}

