%!TEX root ../minutesOfMeeting.tex
%
\thispagestyle{fancy}
\chapter*{Minutes of meeting}


\section*{Call to order}
A meeting between representatives Problematic and the customer of the AreaAware system.\\
\textbf{Location:} Problematic at Finlandsgade 22 8200 Aarhus N, Denmark.\\ Building: Shannon.\\
\textbf{Date:} Friday 04-March-2016. \\
\textbf{Time:} 10:00-10:30.
\section*{Attendees}
\textbf{From Problematic:} Jens Frost Lunding, Kristoffer Sloth Gade, Ivan Bjerring Hansen \& Kim Lykke Johansen.\\
\textbf{Customer:} Casper Thule Hansen.\\\\
\textbf{Not present:} From problematic: Jeppe Blixenkrone-Møller, Simon Østergaard Kristensen, Simon Bækkegaard \& René Rotvig Jensen.\\\\
\textbf{Meeting Moderator \& Time keeper:} Kim Lykke Johansen. \\
\textbf{Minutes Taker:} Kim Lykke Johansen.

\section*{Feedback on VP}
\begin{itemize}
    \item Section 1.1: "This document is applies..." Again!
    \\ \textbf{Correction ID: CID-AA-20160304-01}
        
    \item Section 1.4: Missing reference to the STD.
    \\ \textbf{Correction ID: CID-AA-20160304-02}
    
    \item Missing a test to ensure that our training leaves the customers employees capable of operating the system correctly.
    Possibly a field test with Problematic as support.
    \\ \textbf{Correction ID: CID-AA-20160304-03}
    
    \item Anomaly 3.1: Only covers multiple components, should be rewritten to cover single components as well.
    \\ \textbf{Correction ID: CID-AA-20160304-04}
    
    \item Missing Procedure and verification matrix.
    \\ \textbf{Correction ID: CID-AA-20160304-05}
\end{itemize}

\section*{Feedback on STD}
\begin{itemize}
    \item Section 1.1: "This document is applies..." AGAIN!!
    \\ \textbf{Correction ID: CID-AA-20160304-06}
    
    \item Chapter 3: purpose: TCTA-02a describe with units such as Dismounted and HQ, instead of commanders.
    \\ \textbf{Correction ID: CID-AA-20160304-07}
    
    \item Missing description of who is suppose to perform the tests.
    \\ \textbf{Correction ID: CID-AA-20160304-08}
    
    \item It should be clear that the preparations maps 1-1 or they should be lists for each test individually.
    \\ \textbf{Correction ID: CID-AA-20160304-09}
    
    \item TCTA-04: Video message: limits for video size/time?
    \\ \textbf{Correction ID: CID-AA-20160304-10}

    \item Missing network load tests.
    \\ \textbf{Correction ID: CID-AA-20160304-11}    
    
    \item Missing Dismounted tests. These should be presented for the customer even though Problematics subcontractor is responsible.
    \\ \textbf{Correction ID: CID-AA-20160304-12}
\end{itemize}.

\section*{General for all documents}
\begin{itemize}
    \item Relatively good work with all documents, but every document could have benefit from a last read through before submit.
\end{itemize}

\section*{Resubmit}
Nothing.

\section*{Other business}
\begin{itemize}
    \item Presentation: Thule suggests that we show how our product can solve problems. And present a user scenario where our system is better than existing solutions.
\end{itemize}

