\chapter{Purpose}
The purpose of this document is to establish a common understanding of how the interaction between the subcontractor, known as \emph{Company C}, and the primecontractor, known as \emph{Company D or Problematic}, are to be carried out.

\chapter{Official contact information}
The subcontractor, Company C, can be contacted via email at the following address in order to arrange meetings, exchange documents, etc.\\\\

Company C: riccardodl92@gmail.com\\\\

\noindent The subcontractor can contact Problematic via email at the follow address in order to arrange meetings, exchange documents, etc.\\\\

Problematic: kristoffersg@hotmail.com\\\\


\chapter{Responsibilities and authorities}
Every member listed on the front page has the authority to act on his/hers companys' behalf.\\\\

\noindent All formal meetings held between the parties must be documented by a Minutes of Meeting distributed to both parties. 
It will be the subcontractors responsibility to have a Minutes Taker and send a Minutes of Meeting to Problematic within 48 hours of the meeting.


\chapter{Procedure for interaction}
The interactions between the two parties, Company C and Problematic should follow the structure given below:
\begin{enumerate}
    \item Work will be initiated by Problematic delivering a Statement of Work along with a series og requirements for the subsystem, called \emph{AreaAware Dismounted}, of AreaAware that Company C are to deliver.
    \item Based on the Statement of Work and requirements for AreaAware Dismounted, Company C is expected to deliver a proposal of System Requirement Specification(SRS).
    \item Problematic will go over the proposed SRS and call for a meeting to evaluate the SRS.
    \begin{enumerate}
        \item This can lead to a repeat of step 2. and 3. until an agreement have been reach.
    \end{enumerate}
    \item When an agreement upon the SRS have been reached Company C can begin designing the AreaAware Dismounted system and is expected to deliver a Detailed Design Document(DDD) to Problematic.
    \item Problematic will go over the proposed DDD and call for a meeting to evaluate the DDD.
    \begin{enumerate}
        \item This can lead to a repeat of step 4. and 5. until an agreement have been reach.
    \end{enumerate}
\end{enumerate}
The structure given above are some strict points that the interaction must contain.
However correspondence regarding the AreaAware Dismounted system, which are not specified within this structure are allowed, but should also go through the prober emails.\\\\


\chapter{Verification}
The AreaAware Dismounted project is expected to follow the 6 life cycle stages described in table \ref{tab:lifeCycle}.
No stage of the project can be initiated, at the expense of Problematic, without the approval of Problematic.

\myTable{Life cycle stages, their purpose and decision gates.}{tab:lifeCycle}{table/decisionGates}