%!TEX root ../semp.tex
%
\thispagestyle{fancy}
\chapter{Program Planning and Control}
\label{chp:program_plan}


\section{Statements of Work (SOW)}
The main purpose of the SOW is to define liabilities, responsibilities and work agreements between client and service providers.

\subsection{Introduction}
\label{sec:sow_intro}
In a military battlefield the \emph{SitaWare Suite} provides the capability to establish situational awareness, what in other settings may be referred to as a common operations picture (COP).
The project AreaAware wishes to extend these possibilities offered by \emph{SitaWare Suite} to cover civilian scenarios, where actors for police, armed forces, hospitals and emergency management work together to control a crisis situation.
A successful result of this could be a scenario where the commanders from a mobile headquarter can evaluate incoming information, act upon it and possibly dispatch orders or information to relevant actors to respond to by.

\subsection{Objectives}
The objective of Project AreaAware is to deliver a solution capable of fulfilling the successful result described above in \ref{sec:sow_intro}.

\subsection{Scope of Work}
The scope of AreaAware
\todojens{inline}{Mere om hvad}



\section{Organization Structure}
The development of AreaAware will be managed by Problematic.
Hence, it is Problematic that will denote the organization of system engineering through out the project.
The system engineering documents will describe what, when and why different artifacts are expected of the proper stakeholders.
All these documents are provided by Problematic through out the project, expected by the date denoted in the Milestone plan, section \ref{plan:milestone}.\\


\noindent AreaWare product will be designed by Problematic in cooperation with the projects stakeholders.
The full product will be developed by development team of Problematic and by one subcontractor.
To ensure that the project are following the norms and requirments listed in system engineering documents, both team will have a system engineer associated.

%The system engineer role is to ensure the project are following all the norms and requirements listed in the SEMP and \todo{Kravspec}, aswell to support all members of the project regarding design and process.
%The system engineer should also continue write and update all relevant system engineering document for the project.

%The development team role is to implement AreaAware as it is described by the system engineer(s).
%The team consists of various fields, including software architects, software engineers and test engineers.\\

% Subcontractor
%The subcontractor will have one system engineer from Problematic to ensure projects are following all norms and requirements listen the SEMP and \todo{Kravspec}, aswell supporting in case of questions regarding the design and process of the project.



\section{Responsibilities}

\section{Procedures}

\section{Authorities}

\section{Work Breakdown Structure (WBS)}



\section{Milestones}
\label{plan:milestone}
The milestone plan here will denote the deadline the delivery of system engineer documents for the AreaAware project, to its proper stakeholders.
A review will ensure all partners are satisfied with content of these documents.
In case of change of documents content, a new delivery and review should should take place. 
\myTable{Plan for delivery of system engineer documents. The colored cells denote {\color{deadlinecolor} Deadline} and \color{reviewcolor} Review}{tab:milestones}{table/milestone}

\section{Schedules}

\section{Program Events}

\section{Program Technical}

\section{Test Readiness Reviews}

\section{Technical and Schedule Performance Metrics}

\section{Engineering Program Integration}

\section{Interface Plans}
\myTable{Interface Elements}{tab:interfaceElements}{table/interfacePlans.tex}
