%!TEX root = ../PC_DDD.tex

\chapter{Scope}
\label{chp:scope}

\section{Identification \& System overview}
This document applies to a subsystem of F-16 combat aircraft System developed by Company E.
More specific to a pod structure and a Climate Control Unit (CCU) for this pod structure.

The pod structure will be the casing of a self protection system designed for F-16 aircrafts.
The self protection system will be able to detect incoming missiles, fire flares as counter measurement and warn the pilot through an advanced threat display and 3-D Audio Warning.
The 3-D Audio Warning should provide the pilot with better situational awareness and hereby reduce reaction time.

The CCU will be measure the temperature in the pod through a temperature sensor in the pod and adjust it if necessary to keep a safe operating temperature for the electronic equipment in the pod.


\section{Document overview}
This document describes how the pod and the CCU will be structured to satisfy the requirements specified in the following documents:
\begin{itemize}
    \item \pcsow
    \item \momPrimeOne
\end{itemize} 
Chapter \ref{chp:system-wide} describes system wide decisions regarding design of system components. 
After this chapter \ref{chp:architectural} gives an architectural design of the pod and the CCU, which identifies system components, describes how the system components interact. 
Section \ref{sec:arch_interface} defines the interface design between the system and the system components describe within this document.

\section{Referenced documents}
All the referenced documents are listed below.
\begin{itemize}
    \item \pcsow
    \item \momPrimeOne
\end{itemize}