\label{chp_qualityProvision}
\chapter{Quality provision}
For each requirement explained in chapter \ref{chp_requirements} this chapter will define qualification methods on how verification shall be done.

The chapter contains two tables, one for describing the different qualification methods, and the other describing how each requirement is qualified.

\begin{longtable}{| p{4.2cm}  | p{7.8cm} |  }
	\hline
	\textbf{Qualification Method}	& \textbf{Descriptin} \\ \hline
	Demonstration					& Qualification of the requirement is done by demonstration. \\ \hline
	Test							& Qualification of the requirement is verified by a test.\\ \hline
	Analysis						& Qualification of the requirement is verified by a through analysis. \\ \hline
	Inspection						& Qualification of the requirement is done by an inspection. \\ \hline
	Contract						& Qualification of the requirement is verified through a contract. \\ \hline
\end{longtable}

\begin{longtable}{| p{2.4cm}  | p{2.6cm} | p{6.6cm} |  }
	\hline
	\textbf{System requirement}	& \textbf{Qualification method} & \textbf{Description} \\ \hline
	TA-01	& Demonstration	& The system shall show a demographic overview of crisis situation \\ \hline
	TA-02	& Demonstration	& The system shall send text information to platform employed by the Emergency Responders. \\ \hline
	TA-03	& Demonstration	& The system shall send voice information to platform employed by the Emergency Respondes. \\ \hline
	TA-04	& Demonstration	& The system shall send video and voice information to platform employed by the Emergency Respondes. \\ \hline
	TA-05	& Demonstration	& The system shall show coordinate of each Emegency Responder. \\ \hline
	TA-06	& Demonstration	& The commander shall be able to create a custom event as an Emegency Responder. \\ \hline
	TA-07	& Demonstration	& The system shall be able to show focus on various sources and types og information. \\ \hline
	TA-08	& Demonstration	& The commander shall be able to biew a history of events. \\ \hline
	NF-01	& Inspection	& The system should follow the interface defined by the SINE network. \\ \hline
	NF-02	& Inspection	& The system will extend the capabilities of the SINE network, by using the internet. \\ \hline
	NF-03	& Test			& The communication from AreaAware is encrypted. \\ \hline
	NF-04	& Test			& The system can operate in temperatures from -10 to 50 degrees. \\ \hline
	NF-05	& Inspection	& AreaAware HQ client processor shall be i3, 2.0 Ghz. \\ \hline
	NF-06	& Inspection	& AreaAware HQ client shall be Intel HD 4000. \\ \hline
	NF-07	& inspection	& AreaWaare HQ client ram shall be 2 Gb ram. \\ \hline
	NF-08	& inspection	& AreaAware HQ client shall have 20 Gb free harddisk space. \\ \hline
	NF-09	& Inspection	& AreaAware HQ client browser shall support ECMAScript 5 and HTML 5 \\ \hline
	NF-10	& Inspection	& AreaAware HQ client shall have a microphone \\ \hline
	NF-11	& Inspection	& AreaAware HQ client shall have a webcam \\ \hline
	NF-12	& Inspection	& AreaAware HQ shall have LAN with 16-port switch. \\ \hline
	NF-13	& Test			& AreaAware HQ shall be powered by 220 Volt. \\ \hline
	NF-14	& Inspection	& AreaAware HQ shall be SINE certified. \\ \hline
	NF-15	& Demonstration	& AreaAware HQ communicates through the SINE network. \\ \hline
	NF-16	& Demonstration	& AreaAware HQ uses LTE to extend the SINE network capabilities. \\ \hline
	NF-17	& Test			& AreaAware HQ must have a connection available from either SINE or the internet at 100kbit/s. \\ \hline
	NF-18	& Test			& AreaAware HQ weighs no more than 3 kilograms, incl. box and cables. \\ \hline
	NF-19	& Test			& AreaAware HQ has the dimensions 10cmx40cmx20cm. \\ \hline
	NF-20	& Contract		& 24/7 access to Service Centre. \\ \hline
	NF-21	& Contract		& A user manual follows with the system. \\ \hline
	NF-22	& Contract		& 2-day training availible for the user of AreaAware HQ. \\ \hline
	NF-23	& Demonstration	& The system i availible as a web application in browsers supporting ECMAScript 5 and HTML5. \\ \hline
	NF-25   & Test          & The system must log event registration, start and end of information distribution and coordinates of Emergency Responders \\ \hline
	
\end{longtable}